Progress report

### 2018-06-10 Report/arne-conference.Rmd
updates to smoothing process

---
title: "Conference output"
author: "Lukáš 'hejtmy' Hejtmánek"
date: "3 May 2018"
output: html_document
---

@@

## PER BLOCK
```{r warning=F, echo=F}
make_graph(conference_walk_all, "condition", "min_norm_distance", "exp_block_id") + ylab("Average normalised trial distance") + xlab("condition") + scale_fill_discrete(name = "Block")

make_graph(conference_walk_all, "condition", "min_norm_time", "exp_block_id") + ylab("Average normalised trial duration") + xlab("condition") + scale_fill_discrete(name = "Block")

make_graph(conference_walk_all, "condition", "errors", "exp_block_id")+ ylab("Average number of errors") + xlab("condition") + scale_fill_discrete(name = "Block")

ggplot(conference_walk_all, aes(x = exp_block_id, y = min_norm_distance, color = factor(condition))) +
  stat_summary(fun.data=mean_cl_normal,position=position_dodge(width=0.1), width = 0.2, geom="errorbar") + 
  stat_summary(fun.y=mean,position=position_identity(), size = 1, geom="line") + 
  ylab("Average normalised trial distance") + xlab("Block") + scale_fill_discrete("Condition")

ggplot(conference_walk_all, aes(x = exp_block_id, y = errors, color = factor(condition))) +
  stat_summary(fun.data=mean_cl_normal,position=position_dodge(width=0.1), width = 0.2, geom="errorbar") + 
  stat_summary(fun.y=mean,position=position_identity(), size = 1, geom="line") + 
  ylab("Number of mistakes in office decision") + xlab("Block") + scale_fill_discrete("Condition")

@@

1 to 4 improvement comparison between VE-real and real-real
```{r}
t.test(df_wide$diff14[df_wide$condition=="ve-real"],df_wide$diff14[df_wide$condition=="real-real"])

>>>>

---
title: "Transfer report"
author: "Lukáš 'hejtmy' Hejtmánek"
date: "4 June 2018"
output: html_document
---

@@

## PER BLOCK
```{r warning=F, echo=F}
make_graph(conference_walk_all, "condition", "min_norm_distance", "exp_block_id") + ylab("Average normalised trial distance") + xlab("condition") + scale_fill_discrete(name = "Block")
make_graph(conference_walk_all, "condition", "min_norm_time", "exp_block_id") + ylab("Average normalised trial duration") + xlab("condition") + scale_fill_discrete(name = "Block")
make_graph(conference_walk_all, "condition", "errors", "exp_block_id")+ ylab("Average number of errors") + xlab("condition") + scale_fill_discrete(name = "Block")
ggplot(conference_walk_all, aes(x = exp_block_id, y = min_norm_distance, color = factor(condition))) +
  stat_summary(fun.data=mean_cl_normal,position=position_dodge(width=0.1), width = 0.2, geom="errorbar") + 
  stat_summary(fun.y=mean,position=position_identity(), size = 1, geom="line") + 
  ylab("Average normalised trial distance") + xlab("Block") + scale_fill_discrete("Condition")
ggplot(conference_walk_all, aes(x = exp_block_id, y = errors, color = factor(condition))) +
  stat_summary(fun.data=mean_cl_normal,position=position_dodge(width=0.1), width = 0.2, geom="errorbar") + 
  stat_summary(fun.y=mean,position=position_identity(), size = 1, geom="line") + 
  ylab("Number of mistakes in office decision") + xlab("Block") + scale_fill_discrete("Condition")

@@

1 to 4 improvement comparison between VE-real and real-real
```{r}
t.test(df_wide$diff14[df_wide$condition=="ve-real"],df_wide$diff14[df_wide$condition=="real-real"])
```

### 2018-06-10 Report/progress-report.Rmd
updates to smoothing process

sop_all <- read.table("../sop.csv", sep=";", header = T, stringsAsFactors = F)
walk_all <- read.table("../walk.csv", sep=";", header = T, stringsAsFactors = F)
load("../multi.data")
load("../settings.data")
df_participants <- settings$participants
df_participants$condition <- paste0(df_participants$First.phase, "-", df_participants$Second.phase)
```

@@

# Per block stats

Condition changes in the 4th block (1-3 1st condtition, 4-6th second condition.) In case of low transfer, we should expect an upward peak in the 4th block

>>>>

sop_all <- read.table("../sop.csv", sep=";", header = T, stringsAsFactors = F)
walk_all <- read.table("../walk.csv", sep=";", header = T, stringsAsFactors = F)
#load("../multi.data")
load("../settings.data")
df_participants <- settings$participants
df_participants$condition <- paste0(df_participants$First.phase, "-", df_participants$Second.phase)
```

@@

# Per block stats
Condition changes in the 4th block (1-3 1st condtition, 4-6th second condition.) In case of low transfer, we should expect an upward peak in the 4th block

Absolute distance to the goal per block.
```{r, echo = F,warning=FALSE}
ggplot(walk_all, aes(x = condition, y = distance, fill=factor(exp_block_id))) +
  stat_summary(fun.data=mean_cl_normal,position=position_dodge(0.95),geom="errorbar") + 
  stat_summary(fun.y=mean,position=position_dodge(width=0.95),geom="bar")
```
